---
title: "LeapsModel_BirdsOnly_20230905"
author: "Josee Rousseau"
date: "2023-09-05"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
  html_notebook:
    fig_caption: no
    toc: yes
    toc_depth: 3
    toc_float: yes
always_allow_html: yes
---


Program name:     LeapsModel_BirdsOnly_20230905.rmd 

Program location: ./Programs/BioIndicator/Modelling

Program goal:     Model what bird predicts bees the best, using subsets of predictors for all datasets

Last modified:		October 18, 2023, by Josee Rousseau


```{r libraries, echo = FALSE, warning = FALSE, message = FALSE}

library(here)
library(leaps)
library(caret)
library(purrr)
library(dplyr)
library(tidyverse)
library(jtools)
library(car)
library(sf)
library(spData)
library(raster)
library(purrr)
library(ebirdst)
library(stars)
library(terra)
library(zoom)
library(corrplot)

`%ni%` <- Negate(`%in%`)
options(scipen = 999)

```
&nbsp;     
 
#### Function to run a leaps model for each subset
```{r}

runLeapsSubModels.fct <- function(DFshuffle) {
  
  ### Shuffle the variables in the dataframe
  df.shuffled <- df[ , c(1, sample(2:ncol(df)))] 
  
  ### Seperate the predictors in N groups
  varGroups <- data.frame(var = 2:numCols, group = as.numeric(cut_number(2:numCols, numSubsets)))
  subDF <- 1:numSubsets
  
  ### Run models for each subset of the data
  run.subModels.fct <- function(subDF) {
    
    df.sub <- df.shuffled[, c(1, varGroups$var[which(varGroups$group == subDF)])]
    
    m.10 <- regsubsets(beeResponse ~ ., data = df.sub,
                       nvmax = numBestVar,   # NULL for no limit on number of variables
                       nbest = 1,      # 1 best model for each number of predictors
                       method = "exhaustive",
                       really.big = TRUE)
    
    ### Ouput some results and export
    summary.10 <- summary(m.10)
    coef.10 <- as.data.frame(coef(m.10, 1:dim(summary.10$which)[1])[numBestVar][[1]])
    results.10 <- list(df.shuffled, m.10, summary.10, coef.10, df.sub)

    ### Extract the estimates and significance for the predictors
    spp.10 <- summary.10$which[numBestVar,]
    df.10.spp <- df.sub[, c(spp.10)]
    m.lm.10 <- lm(beeResponse ~ ., data = df.10.spp)
    ( lm.10 <- summary(m.lm.10) )
    
    coefs <- data.frame(round(summary(m.lm.10)$coefficients, 4))
    coefs.df <- data.frame(model = nameDF, predictors = row.names(coefs), 
                           Estimate = coefs$Estimate, StdError = coefs$Std..Error,
                           tValue = coefs$t.value, significance = coefs$Pr...t.., 
                           rSquared = summary(m.lm.10)$adj.r.squared, dfShuffle <- DFshuffle, subDF = subDF)
    
    return(coefs.df)
  }
  
  subResult <- map_dfr(subDF, run.subModels.fct)
  
  return(subResult)
  
}

```
&nbsp;     
 
#### Response: Mean number of species per survey
#### Select best predictors using data from years 2007 to 2021, minimum 30 bees, 20% prevalence birds    
```{r}

nameDF <- "BeesMin30_Birds20pct_LandCovers20pct_2007to2021"

nameFile <- "BeesMin30_Birds20pct_LandCovers20pct_2007to2021_no1beeSurv_Resid30BeesCells"

df <- read.csv(here("Data", "BioIndicator", paste0(nameDF, "_no1beeSurv_Resid30BeesCells_20231017.csv")))

### Format df, selecting apprepriate response
df <- df[,c(2:dim(df)[2])]

### Change name of selected standardized response to "beeResponse"
colnames(df)[1] <- "beeResponse"

### Scale the predictors
numCols <- dim(df)[2]
df[,c(2:numCols)] <- scale(df[,c(2:numCols)], center = TRUE, scale = TRUE) 

### Create birds only or land covers only dataframes
# names(df)
df <- df[ , c(1:80)] # Birds only
# df <- df[ , c(1, 81:numCols)] # Land covers only

### Numbers
DFshuffle <- 1:1000
numBestVar <- 3
numCols <- dim(df)[2] - 1
numSubsets <- ifelse(numCols <= 35, 1,
                     ifelse(numCols > 35 & numCols < 70, 2,
                            ifelse(numCols >= 70 & numCols < 100, 3,
                                   ifelse(numCols >= 100 & numCols < 125, 4, 5))))
  
### Run the model that subset df and extract best predictors per subset
set.seed(2023)
allResults <- map_dfr(DFshuffle, runLeapsSubModels.fct)

### Extract list of best predictors
birds.lc.predictors <- unique(allResults$predictors)
birds.lc.predictors <- birds.lc.predictors[!birds.lc.predictors =="(Intercept)"] # 44 predictors using 1000 shuffles

### Number of times each predictor were selected out of number of DFshuffle
numSelection <- allResults %>%
  group_by(predictors) %>%
  summarise(nModels = n(), meanCoef = mean(Estimate), sdCoef = sd(Estimate), .groups = 'drop')

```
&nbsp;     
 
#### Uses the predictors selected by subseting the variables, identify the most correlated predictors with bee richness in 100 models   
```{r}

### Select the predictors within df
df.preds <- df[, c("beeResponse", birds.lc.predictors)]

### What is the number of predictor considered, if less than 10?
numPreds <- ifelse(dim(df.preds)[2] < 11, dim(df.preds)[2] - 1, 10)

### Run model and save results
set.seed(8617)
m.30 <- regsubsets(beeResponse ~ ., data = df.preds,
                   nvmax = 10,   # NULL for no limit on number of variables
                   nbest = 100,      # 1 best model for each number of predictors
                   method = "exhaustive",
                   really.big = TRUE)

### Ouput some results
s.30 <- summary(m.30)
# coef(m.30, 1:dim(s.30$which)[1])

### Extract the best models with 10 predictors
extractPredictors.fct <- function(modelNum) {
# modelNum <- 860

  ### Extract the predictors
  spp.30 <- s.30$which[modelNum,]
  df.30.spp <- df.preds[, c(spp.30)]
  m.lm.30 <- lm(beeResponse ~ ., data = df.30.spp)
  lm.30 <- summary(m.lm.30)
  
  ### Format
  df <- data.frame(t(coef(lm.30)[,1]))
  
  return(df)
}

modelNum <- c(845:944)
results <- map_dfr(modelNum, extractPredictors.fct)

### Calculate the number of times each predictor is selected
numModelsPerPred <- data.frame(colSums(!is.na(results)))
numModelsPerPred$predictors <- row.names(numModelsPerPred)
write.csv(numModelsPerPred, here("Results", "BioIndicator", "numModels_out100_predictorsSelected_birdsOnly_20231018.csv"), row.names = FALSE)

### Ouput some results and export
results.30 <- list(df, m.30, s.30, df.preds, results, numModelsPerPred)
saveRDS(results.30, here("Results", "BioIndicator", paste0("leapModels_birdsOnly_", nameFile, "_20231018.rds")))
# results.30 <- readRDS(here("Results", "BioIndicator", paste0("leapModels_birdsOnly_", nameFile, "_20231018.rds")))

remove(DFshuffle, numBestVar, numCols, numSubsets, numSelection, birds.lc.predictors)
```
&nbsp;     
 
#### Predict bee richness value for each location from the each of the 100 models and extract a mean bee richness per location
```{r}

### Read results, if needed
nameFile <- "BeesMin30_Birds20pct_LandCovers20pct_2007to2021_no1beeSurv_Resid30BeesCells"
results.30 <- readRDS(here("Results", "BioIndicator", paste0("leapModels_birdsOnly_", nameFile, "_20231018.rds")))
predsEstimates <- results.30[[5]]
predsEstimates[is.na(predsEstimates)] <- 0

### List all the birds and land covers that were selected at least once in the 100 models
# names(predsEstimates)
birds <- c("Carolina Wren", "Northern Cardinal", "Wood Thrush", "Scarlet Tanager", "Chipping Sparrow", 
           "Blue Jay", "Warbling Vireo", "Orchard Oriole", "Common Yellowthroat", "Gray Catbird", 
           "Black-capped Chickadee", "Downy Woodpecker", "White-breasted Nuthatch", "American Crow", "Dickcissel", 
           "Yellow-billed Cuckoo", "Cliff Swallow", "Blue Grosbeak", "American Redstart", "American Robin", 
           "Song Sparrow", "Ruby-throated Hummingbird", "Red-bellied Woodpecker", "House Sparrow", "American Goldfinch", 
           "Brown Thrasher", "Rose-breasted Grosbeak") # 27 species

### Change the species names to the 6-letter codes
clement <- read.csv("/Volumes/BirdsBees/Data/eBird/NEW_eBird-Clements-v2022-integrated-checklist-October-2022.csv")
birds.6L <- clement$SPECIES_CODE[which(clement$PRIMARY_COM_NAME %in% birds)]
birds.6L <- birds.6L[c(11, 24, 14, 23, 18, 6, 5, 20, 21, 12, 8, 4, 10, 7, 27, 1, 9, 26, 22, 15, 19, 2, 3, 16, 17, 13, 25)]

### Read the status grid to eastern USA
east.grid <- readRDS(here("Data", "BioIndicator", "birdStatusGrid_4326_EastUSA_3kmGridAndBuffer_20231017.rds"))
# east.grid <- readRDS(here("Results", "BioIndicator", "Maps", "birdStatusGrid_4326_EastUSA_3km_20230725.rds"))

### East grid vector file as a spatvector
east.grid2 <- vect(east.grid) 

### Import one bird layer to extract projection and project our grid to that
eust <- load_raster("/Volumes/BirdsBees/Data/eBird/StatusTrends/2023/2021/eursta", product = "abundance",   # count
                                 period = "seasonal", metric = "mean", 
                                 resolution = "hr")
east.grid3 <- terra::project(east.grid2, crs(eust))

#########################################################
### Import bird status for species selected in model ####
#########################################################

### Import status data associated with the indicator species
import.spp.fct <- function(spp) {
# spp <- "bkcchi"
# spp <- "warvir"
  
  print(spp)
  
  ### Extract the breeding abundance data for the species
  path_status <- paste0("/Volumes/BirdsBees/Data/eBird/StatusTrends/2023/2021/", spp) 
  abund <- load_raster(path_status, product = "abundance",   # count
                                 period = "seasonal", metric = "mean", 
                                 resolution = "hr")
  
  ### Extract the breeding season for migrants and year-round season for residents
  abund <- if (any(abund@ptr$names == "breeding")) {
    abund <- abund[[abund@ptr$names == "breeding"]]
  } else {
    abund <- abund[[abund@ptr$names == "resident"]]
  } 

  ### Crop the abundance layer to region
  east.crop <- crop(abund, east.grid3, mask = TRUE)
  
  return(east.crop)  
} 

allspp.30 <- map(birds.6L, import.spp.fct) 

########################################################################################
### For each model (n = 100), calculate the predicted bee richness at each location ####
########################################################################################

predictMap.perModel.fct <- function(modelRow){
# modelRow <- 10 
  df <- predsEstimates[modelRow,]
  
  # names(predsEstimates)
  mapBee <- df[,1] +
    (df[,2] * allspp.30[[1]]) +
    (df[,3] * allspp.30[[2]]) +
    (df[,4] * allspp.30[[3]]) +        
    (df[,5] * allspp.30[[4]]) +
    (df[,6] * allspp.30[[5]]) +
    (df[,7] * allspp.30[[6]]) +      
    (df[,8] * allspp.30[[7]]) +
    (df[,9] * allspp.30[[8]]) +    
    (df[,10] * allspp.30[[9]]) +      
    (df[,11] * allspp.30[[10]]) +
    (df[,12] * allspp.30[[11]]) +
    (df[,13] * allspp.30[[12]]) +
    (df[,14] * allspp.30[[13]]) +
    (df[,15] * allspp.30[[14]]) +    
    (df[,16] * allspp.30[[15]]) +    
    (df[,17] * allspp.30[[16]]) +
    (df[,18] * allspp.30[[17]]) +        
    (df[,19] * allspp.30[[18]]) +        
    (df[,20] * allspp.30[[19]]) +        
    (df[,21] * allspp.30[[20]]) +        
    (df[,22] * allspp.30[[21]]) +        
    (df[,23] * allspp.30[[22]]) +        
    (df[,24] * allspp.30[[23]]) +        
    (df[,25] * allspp.30[[24]]) +        
    (df[,26] * allspp.30[[25]]) +        
    (df[,27] * allspp.30[[26]])  

  return(mapBee)
}

modelRow <- c(1: dim(predsEstimates)[1])
allMaps <- map(modelRow, predictMap.perModel.fct)

### Calculate mean of all maps and SD (SD reflects predictor selection uncertainty)
mapsMean <- app(c(allMaps[[1]],allMaps[[2]],allMaps[[3]],allMaps[[4]],allMaps[[5]],allMaps[[6]],allMaps[[7]],allMaps[[8]],allMaps[[9]],allMaps[[10]],
                  allMaps[[11]],allMaps[[12]],allMaps[[13]],allMaps[[14]],allMaps[[15]],allMaps[[16]],allMaps[[17]],allMaps[[18]],allMaps[[19]],allMaps[[20]],
                  allMaps[[21]],allMaps[[22]],allMaps[[23]],allMaps[[24]],allMaps[[25]],allMaps[[26]],allMaps[[27]],allMaps[[28]],allMaps[[29]],allMaps[[30]],
                  allMaps[[31]],allMaps[[32]],allMaps[[33]],allMaps[[34]],allMaps[[35]],allMaps[[36]],allMaps[[37]],allMaps[[38]],allMaps[[39]],allMaps[[40]],
                  allMaps[[41]],allMaps[[42]],allMaps[[43]],allMaps[[44]],allMaps[[45]],allMaps[[46]],allMaps[[47]],allMaps[[48]],allMaps[[49]],allMaps[[50]],
                  allMaps[[51]],allMaps[[52]],allMaps[[53]],allMaps[[54]],allMaps[[55]],allMaps[[56]],allMaps[[57]],allMaps[[58]],allMaps[[59]],allMaps[[60]],
                  allMaps[[61]],allMaps[[62]],allMaps[[63]],allMaps[[64]],allMaps[[65]],allMaps[[66]],allMaps[[67]],allMaps[[68]],allMaps[[69]],allMaps[[70]],
                  allMaps[[71]],allMaps[[72]],allMaps[[73]],allMaps[[74]],allMaps[[75]],allMaps[[76]],allMaps[[77]],allMaps[[78]],allMaps[[79]],allMaps[[80]],
                  allMaps[[81]],allMaps[[82]],allMaps[[83]],allMaps[[84]],allMaps[[85]],allMaps[[86]],allMaps[[87]],allMaps[[88]],allMaps[[89]],allMaps[[90]],
                  allMaps[[91]],allMaps[[92]],allMaps[[93]],allMaps[[94]],allMaps[[95]],allMaps[[96]],allMaps[[97]],allMaps[[98]],allMaps[[99]],allMaps[[100]]), fun = "mean")
plot(mapsMean)

terra::writeRaster(mapsMean, here("Results", "BioIndicator", "Maps", "mean100Birds_Oct19.tif"), filetype = "GTiff", overwrite = TRUE)

```
&nbsp;     
 
#### Calculate R-squared (model fit) for our models and five-fold validation using locations where we have observed bee data
```{r}

### Import observed bee richness data and save as spatial object
nameFile <- "BeesMin30_Birds20pct_LandCovers20pct_2007to2021_no1beeSurv_Resid30BeesCells"
results.30 <- readRDS(here("Results", "BioIndicator", paste0("leapModels_birdsOnly_", nameFile, "_20231018.rds")))
predsEstimates <- results.30[[5]]
predsEstimates[is.na(predsEstimates)] <- 0
modelRow <- c(1: dim(predsEstimates)[1])
df <- results.30[[1]]
s.100 <- results.30[[3]]

### Function that 
oneFold.pred.fct <- function(oneFold, df.valid) {
# oneFold <- five.folds; df.valid <- df.preds

  ### Extract records not part of the testing sample
  train.DF <- df.valid[which(rownames(df.valid) %ni% as.character(oneFold)), c(1:11)]

  ### Extract records included in one fold, i.e., in the testing sample
  test.DF <- df.valid[which(rownames(df.valid) %in% oneFold), c(1:11)]
  
  ### Create model (like the resulting Leaps model)
  m.train <- lm(beeResponse ~ ., data = train.DF) 
  # summary(m.train)
  
  ### Predict the bees in the testing samples, based on the bird and land covers
  m.test <- m.train %>% predict(test.DF)
  
  ### Create an output dataframe
  predObs <- data.frame(loc = oneFold, obs = test.DF[,c(1)], pred = m.test)
  # print(pred.obs)
 
	return(predObs)
}

### Function that takes each of the 100 models and calculate model fit and five-fold validation
fit.5valid.corr.fct <- function(modelRowID) {
# modelRowID <- 1

  # ### Divide the dataframe into 5 folds
  set.seed(1234)
  five.folds <- createFolds(1:nrow(df), k = 5, list = TRUE, returnTrain = FALSE)

  ### Use only predictors that were selected through leaps, for each model
  m.preds <- predsEstimates[modelRowID, ]
  m.preds <- m.preds[,which(m.preds != 0)]
  m.preds <- names(m.preds[-1])
  df.preds <- df[, c("beeResponse", m.preds)]
  
  ### Calculate the prediction accuracy for each grid cell and fold
  # numPreds <- length(m.preds)
  allFolds <- map2(.x = five.folds, .y = list(df.preds), .f = oneFold.pred.fct)
  obsPred <- bind_rows(allFolds, .id = "Fold")
  
  ### Extract model fit per model
  m.lm <- lm(beeResponse ~ ., data = df.preds)
  beePredict <- m.lm %>% predict(df.preds)
  beePredict2 <- data.frame(modelNum = modelRowID, cellNum = c(1:nrow(df.preds)), obs = df.preds$beeResponse, preds = beePredict)

  ### Assess predictors' multicollinearity
  vif.preds <- vif(m.lm)
  cor.preds <- corrplot(cor(df.preds[,-1]), method = "number")
  cor.preds <- cor.preds$corrPos

  ### Return results
  results <- list(obsPred, beePredict2, vif.preds, cor.preds, df.preds)
  return(results)
  # remove(modelRow, five.folds, m.preds, df.preds, allFolds, obsPred, R2.100, m.lm, lm.modelNum, m.R2, m.adj.R2)
}

fit.valid.corr <- map(modelRow, fit.5valid.corr.fct)
saveRDS(fit.valid.corr, here("Results", "BioIndicator", "BirdsOnly_modelFit_5foldValid_VIF_20231019.rds"))
# fit.valid.corr <- readRDS(here("Results", "BioIndicator", "BirdsOnly_modelFit_5foldValid_VIF_20231019.rds"))

### Average all model predictions (created using full sample), across 100 models
fullSample.obs.preds <- do.call(rbind, lapply(fit.valid.corr, function(element){
  element[[2]] }))
mean.preds.perCell <- fullSample.obs.preds %>%
  # gather(key = cellNum, value = "cellValue") %>%
  group_by(cellNum) %>%
  summarise(meanPred = mean(preds), obs = mean(obs), .groups = "drop")
modelFit.r2 <- 1 - sum((mean.preds.perCell$meanPred - mean.preds.perCell$obs)^2) / sum((mean.preds.perCell$obs - mean(mean.preds.perCell$obs))^2)
# print(paste("Model fit r-squared is", round(mean.all.m.fit.rsq, 4), "+/- SD", round(sd.all.m.fit.rsq, 4)))

### Calculate the average prediction per location, across the 100 models using five-fold validation predictions
all.obsPred <- lapply(fit.valid.corr, '[[', 1) 
all.obsPred <- bind_rows(all.obsPred, .id = "modelNum") 
meanPred.perLoc <- all.obsPred %>%
  group_by(loc) %>%
  summarise(meanPred = mean(pred), obsAtLoc = mean(obs), .groups = "drop") %>%
  mutate(diff = abs(obsAtLoc - meanPred))

### Calculate validation r-square
val.R2 <- 1 - sum((meanPred.perLoc$meanPred - meanPred.perLoc$obsAtLoc)^2) / sum((meanPred.perLoc$obsAtLoc - mean(meanPred.perLoc$obsAtLoc))^2)

### Assess the VIF value associated with each model and extract those 
all.vif <- lapply(fit.valid.corr, '[[', 3) 
all.vif <- bind_rows(all.vif, .id = "ID")
max(all.vif[,c(2:28)], na.rm = TRUE) # 2.332758
all.vif.high <- all.vif[which(all.vif[,-1] > 5),] # None of the models have predictors with a VIF value higher than 5

### Assess the correlation between predictors within each model
all.corr <- lapply(fit.valid.corr, '[[', 4) 
all.corr <- bind_rows(all.corr, .id = "ID")
all.corr <- all.corr[which(all.corr$xName != all.corr$yName),]
# Here are the most correlated variables, and their model number
# NorthernCardinal - CarolinaWren - 0.6304146
# RedBelliedWoodpecker - NorthernCardinal - 0.5993954
# RedBelliedWoodpecker - CarolinaWren - 0.5134030

```
&nbsp;     
 
#### For each of the 100 lm models, calculate the uncertainty associated with bee richness, considering both predictor selection uncertainty and predictor coefficient uncertainty
```{r}

### Rasterize the idCells info
grid.rast <- rasterize(east.grid3, mapsMean, field = "idCells", cover = FALSE)

### Create a stack of rasters that are used at least once in the models
list.rasters <- c(allspp.30, grid.rast)
stack.preds <- rast(list.rasters)
# terra::writeRaster(stack.preds, here("Results", "BioIndicator", "Maps", "stackPreds.tif"), filetype = "GTiff", overwrite = TRUE)

### Create dataframe from stack of rasters
df.aoi.preds <- as.data.frame(stack.preds, row.names = FALSE, cells = TRUE, na.rm = TRUE)
names(df.aoi.preds) <- c("id", "CarolinaWren", "NorthernCardinal", "WoodThrush", "ScarletTanager", "ChippingSparrow", 
           "BlueJay", "WarblingVireo", "OrchardOriole", "CommonYellowthroat", "GrayCatbird", 
           "BlackCappedChickadee", "DownyWoodpecker", "WhiteBreastedNuthatch", "AmericanCrow", "Dickcissel", 
           "YellowBilledCuckoo", "CliffSwallow", "BlueGrosbeak", "AmericanRedstart", "AmericanRobin", 
           "SongSparrow", "RubyThroatedHummingbird", "RedBelliedWoodpecker", "HouseSparrow", "AmericanGoldfinch", 
           "BrownThrasher", "RoseBreastedGrosbeak", "idCells")

### Save object as shapefile to assess in QGIS
df.aoi.preds.map <- merge(east.grid3, df.aoi.preds, by = "idCells")
write.csv(df.aoi.preds, here("Results", "BioIndicator", "predictors_birdsOnly_studyArea_20231019.csv"), row.names = FALSE)
writeVector(df.aoi.preds.map, here("Results", "BioIndicator", "Maps", "predictors_birdsOnly_studyArea_20231019.shp"),
            filetype = "ESRI Shapefile", overwrite = TRUE) # big diagonal squares

### Extract list of linear model summaries
s.30 <- results.30[[3]]
df.preds <- results.30[[4]]

extractPredictors.SE.fct <- function(modelNum) {
# modelNum <- 860
  
  ### Extract the predictors
  spp.30 <- s.30$which[modelNum,]
  df.30.spp <- df.preds[, c(spp.30)]
  m.lm.30 <- lm(beeResponse ~ ., data = df.30.spp)
  lm.30 <- summary(m.lm.30)
  
  ### Predict
  preds.lm <- predict(m.lm.30, newdata = df.aoi.preds, se.fit = TRUE)  # select dataframe with all grid cells for wall-to-wall map of predictions

  ### Select bee richness at quantile value
  z <- rnorm(1, 0, 1)
  values <- preds.lm$se.fit * z + preds.lm$fit
  
  ### Return
  df <- data.frame(idCells = df.aoi.preds$idCells, locID = c(1:length(values)), modelNum = modelNum, pbBee = values, meanBee = preds.lm$fit, seBee = preds.lm$se.fit) # pb for parametric bootstrap
  
  return(df)
}

modelNum <- c(845:944)
results <- map_dfr(modelNum, extractPredictors.SE.fct) # This take a somewhat long time to run

### Calculate the confidence interval at each location (this also takes a somewhat long time to run)
CI.bees <- results %>%
  group_by(idCells) %>%  
  summarise(lowCI = quantile(pbBee, 0.05), highCI = quantile(pbBee, 0.95), meanBee = mean(pbBee), sdBee = sd(pbBee), .groups = "drop") %>%
  mutate(coefVar = sdBee / abs(meanBee))

### Export results
write.csv(CI.bees, here("Results", "BioIndicator", "beeRich_uncertainty_atLocs_birdsOnly_20231019.csv"), row.names = FALSE)
CI.bees.map <- merge(east.grid3, CI.bees, by = "idCells")
writeVector(CI.bees.map, here("Results", "BioIndicator", "Maps", "beeRich_uncertainty_atLocs_birdsOnly_20231019.shp"),
            filetype = "ESRI Shapefile", overwrite = TRUE) 
CI.bees.map.cv.rast <- rasterize(CI.bees.map, mapsMean, field = "coefVar", cover = FALSE)
terra::writeRaster(CI.bees.map.cv.rast, here("Results", "BioIndicator", "Maps", "beeBirdCoefVar_Oct19.tif"), filetype = "GTiff", overwrite = TRUE)
plot(CI.bees.map.cv.rast)
CI.bees.map.sd.rast <- rasterize(CI.bees.map, mapsMean, field = "sdBee", cover = FALSE)
terra::writeRaster(CI.bees.map.sd.rast, here("Results", "BioIndicator", "Maps", "beeBirdSD_Oct19.tif"), filetype = "GTiff", overwrite = TRUE)
CI.bees.map.lowCI.rast <- rasterize(CI.bees.map, mapsMean, field = "lowCI", cover = FALSE)
terra::writeRaster(CI.bees.map.lowCI.rast, here("Results", "BioIndicator", "Maps", "beeBirdLowCI_Oct19.tif"), filetype = "GTiff", overwrite = TRUE)
CI.bees.map.highCI.rast <- rasterize(CI.bees.map, mapsMean, field = "highCI", cover = FALSE)
terra::writeRaster(CI.bees.map.highCI.rast, here("Results", "BioIndicator", "Maps", "beeBirdHighCI_Oct19.tif"), filetype = "GTiff", overwrite = TRUE)

```
