---
title: "Extract_eBirdObsChecklists_InGrid3km_20230822"
author: "Josee Rousseau"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
  html_notebook:
    fig_caption: no
    toc: yes
    toc_depth: 3
    toc_float: yes
always_allow_html: yes
---


Program name:     Extract_eBirdObsChecklists_InGrid3km_20230822.Rmd

Program location: "./Programs/BioIndicator/Extract_BeeBird_data"

Program goal:     Extract bird checklists that overlap grid cells with bee data. 

Last modified:		October 17, 2023 by Josee Rousseau


```{r libraries, echo = FALSE, warning = FALSE, message = FALSE}

library(here)
library(dplyr)
library(tidyr)
library(auk)
library(lubridate)
library(purrr)
library(sf)
library(spData)
library(chunked)

'%notin%' <- Negate('%in%')

```
&nbsp;     
 
#### Import needed datasets
```{r}

### Identify the eBird observation and sampling EBD
ebd_obs <- auk_ebd("/Volumes/BirdsBees/Data/eBird/World/ebd_relApr-2022/ebd_relApr-2022.txt")
ebd_sampl <- auk_sampling("/Volumes/BirdsBees/Data/eBird/World/ebd_sampling_relApr-2022/ebd_sampling_relApr-2022.txt")
                          
### Identify the output file names
samplEast <- "/Volumes/BirdsBees/Data/eBird/Filtered/eBirdSamples_Eastern_2007to2021_20230301.txt"
obsEast <- "/Volumes/BirdsBees/Data/eBird/Filtered/eBirdObs_Eastern_2007to2021_20230307.txt"
obsEast_small <- "/Volumes/BirdsBees/Data/eBird/Filtered/eBirdObs_Eastern_FewCols_2007to2021_20230307.txt"

### List of states
states <- c("West Virginia", "Virginia","Kentucky", "Tennessee", "North Carolina", "South Carolina", "Georgia",
            "Alabama", "Maryland", "Mississippi", "Connecticut", "Delaware", "Massachusetts", "New Hampshire",
            "New Jersey", "New York", "Pennsylvania", "Rhode Island", "Vermont", "District of Columbia",
            "North Dakota", "South Dakota", "Nebraska", "Kansas", "Minnesota", "Iowa", "Missouri", "Wisconsin",
            "Illinois", "Michigan", "Indiana", "Ohio", "Arkansas", "Oklahoma")
states.abr <- c("US-WV", "US-VA", "US-KY", "US-TN", "US-NC", "US-SC", "US-GA", 
                "US-AL", "US-MD", "US-MS", "US-CT", "US-DE", "US-MA", "US-NH", 
                "US-NJ", "US-NY", "US-PA", "US-RI", "US-VT", "US-DC", 
                "US-ND", "US-SD", "US-NE", "US-KS", "US-MN", "US-IA", "US-MO", "US-WI", 
                "US-IL", "US-MI", "US-IN", "US-OH", "US-AR", "US-OK")

### Import grid used as mask for eBird status
statusEastUSA <- readRDS(here("Data", "BioIndicator", "birdStatusGrid_4326_EastUSA_3kmGridAndBuffer_20231017.rds"))
# 
# status.grid <- st_read("/Users/jsr293/Documents/GIS_Data/eBird_StatusTrend_Grids/statusGrid_USA_4326.shp")
# 
# ### Crop Raster with Spatial object
# region <- st_transform(us_states, crs = 4326)
# 
# ### Select states covering our region of interest
# states <- c("West Virginia", "Virginia","Kentucky", "Tennessee", "North Carolina", "South Carolina", "Georgia",
#             "Alabama", "Maryland", "Mississippi", "Connecticut", "Delaware", "Massachusetts", "New Hampshire",
#             "New Jersey", "New York", "Pennsylvania", "Rhode Island", "Vermont", "District of Columbia",
#             "North Dakota", "South Dakota", "Nebraska", "Kansas", "Minnesota", "Iowa", "Missouri", "Wisconsin",
#             "Illinois", "Michigan", "Indiana", "Ohio", "Arkansas", "Oklahoma") 
# east.USA <- region[which(region$NAME %in% states), ]
# 
# ### Dissolve the region as one polygon
# regionDiss <- east.USA %>% 
# 	 st_union() %>%
# 	 st_sf()
# 
# ### Crop the status grid to contiguous USA
# statusEastUSA <- st_crop(status.grid, regionDiss)

### Grid cells with bees (any number of bees; based on bird status grid).
grid.bees <- readRDS(here("Data", "BioIndicator", "bees_standardized_meanPerSurvey_no1beeSurv_2007to2021_20231017.rds"))

### Check how many locations have a sufficient sample size
bee.locs <- grid.bees[which(grid.bees$nBees >= 30 | grid.bees$nSurveys >= 2),] 
# 3,076 locations (of which we have bird data for 2,585 locations, or 84%)

# identical(st_crs(grid.bees), st_crs(statusEastUSA)) # TRUE

# remove(status.grid, states, east.USA, regionDiss)

```
&nbsp;     
 
#### Extract eBird samples falling within grid cells with bees
```{r}

### Extract eBird surveys for some states and years
ebd_filters <- ebd_sampl %>%
  auk_state(state = states.abr) %>%
	auk_date(date = c("2007-01-01", "2021-12-31")) %>%
	auk_protocol(protocol = c("Stationary", "Traveling")) %>%
	auk_complete() %>%
  auk_filter(file = samplEast, overwrite = TRUE)

### Import the filtered observation records
f_sampl <- read_sampling(samplEast, unique = FALSE) # 18,768,491 checklists if unique = TRUE; 21,337,614 when using unique = FALSE

### Select observations during breeding season
f_sampl.breed <- f_sampl %>%
  dplyr::mutate(obs_date = as.Date(observation_date), 
                Jul_date = yday(obs_date))

### Select surveys done between mid-May and mid-August                
f_sampl.breed <- f_sampl.breed[which(f_sampl.breed$Jul_date >= 135 &
                                 f_sampl.breed$Jul_date < 227 &  # Select breeding season days:
                                 f_sampl.breed$duration_minutes >= 5 &
                                 f_sampl.breed$duration_minutes <= 300), ]
# 4,458,699 surveys

remove(f_sampl)

### Keep only a few columns to minimize size
f_sampl.breed.cols <- f_sampl.breed[, c("latitude", "longitude", "observation_date", "time_observations_started", "observer_id", "sampling_event_identifier", "protocol_code", "duration_minutes", "effort_distance_km", "group_identifier")] 

### Create spatial object of survey data
f_sampl.breed.cols$Lat <- f_sampl.breed.cols$latitude
f_sampl.breed.cols$Long <- f_sampl.breed.cols$longitude
f_sampl.breed.cols.sf <- st_as_sf(x = f_sampl.breed.cols,
         coords = c("Long", "Lat"),
         crs = 4326)
f_sampl.breed.cols.sf <- st_transform(f_sampl.breed.cols.sf, crs = st_crs(statusEastUSA))

### Make sure the grid is in the same coordinates as the bird samples
# identical(st_crs(grid.bees), st_crs(f_sampl.breed.cols.sf)) # TRUE

### Extract samples in region of interest
survInStates <- st_filter(f_sampl.breed.cols.sf, statusEastUSA) 
# 4,394,881 bird surveys

### Identify the grid cell in which each sampling is located
surv.grid <- sf::st_join(survInStates, grid.bees, join = st_intersects) 

### Keep only sampling that fall within one of the grid cells used in the bee grid (whether there were bees or not)
surv.grid.cell <- surv.grid[which(!is.na(surv.grid$idCells)), ] 
# 4,394,881 samplings 
st_geometry(surv.grid.cell) <- NULL

### Save another version where we have only the grid cells with bird surveys AND bee data
surv.bees.grid <- surv.grid.cell[which(surv.grid.cell$nBees > 0), ] 
# 782,734 sampling in 4,937 grid cells where we have bee data for 2007 to 2021

write.csv(surv.grid.cell, "/Volumes/BirdsBees/Data/eBird/BirdsIndicators_MidSteps/eBirdSampling_withCellID_EastHalfUSA_2007to2021_20231017.csv", row.names = FALSE)
write.csv(surv.bees.grid, "/Volumes/BirdsBees/Data/eBird/BirdsIndicators_MidSteps/eBirdSampling_withCellID_withBeeData_EastHalfUSA_2007to2021_20231017.csv", row.names = FALSE)

### Some cleaning
remove(surv.grid, survInStates, f_sampl.breed.cols, f_sampl.breed.cols.sf, states.abr) # f_sampl.breed, 

```
&nbsp;     
 
#### Remove checklists for observers who submitted 2 or less checklists
```{r}

surv.bees.grid <- read.csv("/Volumes/BirdsBees/Data/eBird/BirdsIndicators_MidSteps/eBirdSampling_withCellID_withBeeData_EastHalfUSA_2007to2021_20231017.csv")

### Select only bird surveys where we have a minimum of 30 bees OR 2 bee surveys
surv.bees.grid.30 <- surv.bees.grid[which(surv.bees.grid$nBees >= 30 | surv.bees.grid$nSurveys >= 2),] # 490,849 surveys
# length(unique(surv.bees.grid.30$idCells)) # 2,668 grid cells

### Identify the number of checklists per observer ID
listsPerObserver <- surv.bees.grid.30 %>%
  group_by(observer_id) %>%
  summarise(nLists = n_distinct(sampling_event_identifier), .groups = "drop")

### Identify observers with 3 or more lists
observers <- listsPerObserver$observer_id[which(listsPerObserver$nLists > 2)] 
# 18,175 observers if min 30 bees

### Keep only observations make by the observers with 3 or more checklists
surv.bees.grid.30.obs <- surv.bees.grid.30[which(surv.bees.grid.30$observer_id %in% observers), ] # 469,310 checklists
# length(unique(surv.bees.grid.30.obs$idCells)) # 2,609 grid cells

```
&nbsp;     
 
#### Extract the eBird observations associated with the checklists above
```{r}

### Extract eBird observations for the selected states and years
ebd_filters <- ebd_obs %>%
  auk_state(state = states.abr) %>%
	auk_date(date = c("2007-01-01", "2021-12-31")) %>%
	auk_protocol(protocol = c("Stationary", "Traveling")) %>%
	auk_complete() %>%
  auk_filter(file = obsEast, overwrite = TRUE)

### Reduce the size of the eBird observation file by keeping only a few columns
ebd_cols <- c("global unique identifier", "common name", "scientific name", "observation count",
              "state code", "locality id", "latitude", "longitude",
              "observation date", "time observations started", "observer id", "sampling event identifier" ,
              "protocol code", "duration minutes", "effort distance km", "group identifier")

f_obs <- auk_ebd(obsEast) %>%
  auk_select(select = ebd_cols, file = obsEast_small)

### Select only eBird observation that match the selected eBird sampling
ebd_obs_atBees <- read_table_chunkwise(obsEast_small, chunk_size = 5000000, sep = "\t")  %>%
  inner_join(surv.bees.grid.30.obs, by = c("SAMPLING.EVENT.IDENTIFIER" = "sampling_event_identifier")) %>%
  write_csv_chunkwise(file = "/Volumes/BirdsBees/Data/eBird/BirdsIndicators_MidSteps/eBirdObsSampl_atGridWith30Bees_EastUSA_2007to2021_20231017.csv", row.names = FALSE)
 
remove(f_sampl.breed, surv.grid.cell, statusEastUSA, listsPerObserver, ebd_sampl, ebd_obs_atBees, ebd_obs, observers, surv.bees.grid, surv.bees.grid.30, surv.bees.grid.30.obs, grid.bees)

### Import the selected observations
surveysObs1 <- read.csv("/Volumes/BirdsBees/Data/eBird/BirdsIndicators_MidSteps/eBirdObsSampl_atGridWith30Bees_EastUSA_2007to2021_20231017.csv")
# 9,845,6946 observations

```
&nbsp;     
 
#### Clean up the eBird observations to remove checklists duplicates and keep only species level
```{r}

### Remove duplicated lists
surveysObs2 <- surveysObs1[!duplicated(surveysObs1$group_identifier) & !is.na(surveysObs1$group_identifier),] 
# 43,565
surveysObs1 <- surveysObs1[is.na(surveysObs1$group_identifier),] 
# 7,377,261 records for 2007 to 2021
surveysObs1 <- rbind(surveysObs1, surveysObs2) 
# 7,420,826 records

remove(surveysObs2)

### Remove observations associated with checklists that have an X in them.
surveysObs1$OBSERVATION.COUNT <- as.numeric(as.character(surveysObs1$OBSERVATION.COUNT))
X.checklists <- surveysObs1[which(is.na(surveysObs1$OBSERVATION.COUNT)), ]
X.checklists <- unique(X.checklists$SAMPLING.EVENT.IDENTIFIER) 
# 35,528 checklists have an X in them; 
surveysObs1 <- surveysObs1[which(surveysObs1$SAMPLING.EVENT.IDENTIFIER %notin% X.checklists),] 
# 6,507,240 observations

### Remove duplicate columns and rename to small letters (as needed for auk_ functions)
surveysObs1 <- surveysObs1[, c("COMMON.NAME", "SCIENTIFIC.NAME", "OBSERVATION.COUNT", "OBSERVATION.DATE", "TIME.OBSERVATIONS.STARTED", "DURATION.MINUTES", "EFFORT.DISTANCE.KM", 
                               "PROTOCOL.CODE", "STATE.CODE", "LOCALITY.ID", "LATITUDE", "LONGITUDE", "OBSERVER.ID", "SAMPLING.EVENT.IDENTIFIER", 
                               "GLOBAL.UNIQUE.IDENTIFIER", "GROUP.IDENTIFIER", "idCells")] 
names(surveysObs1) <- c("common_name", "scientific_name", "observation_count", "observation_date", "time_observations_started", "duration_minutes", "effort_distance_km", "protocol_code", "state_code", "locality_id", "latitude", "longitude", "observer_id", "sampling_event_identifier", "global_unique_identifier", "group_identifier", "idCells")
  
### Update subspecies to species taxonomic level (this step takes a somewhat long time ~ 15 minutes)
surveysObs1 <- auk_rollup(surveysObs1)  # 6,451,901 observations
# length(unique(surveysObs1$idCells)) # 2,594 grid cells

### Export eBird data
write.csv(surveysObs1, "/Volumes/BirdsBees/Data/eBird/BirdsIndicators_MidSteps/eBirdObsSampl_clean_atGridWith30Bees_EastUSA_2007to2021_20231017.csv", row.names = FALSE)

```
&nbsp;     
 
#### Assess the prevalence of each species across locations with bee data (i.e., prevalence within surveyed locations).   
#### Select species for which their breeding range covers at least 40% of our study area and that are present in at least 20% of our surveyed locations.    
```{r}
# eBird key to download data: 4lh7ngufqcfb

### Import observations and surveys
# surveysObs1 <- read.csv("/Volumes/BirdsBees/Data/eBird/BirdsIndicators_MidSteps/eBirdObsSampl_clean_atGridWith30Bees_EastUSA_2007to2021_20231017.csv")

### Calculate the number of birds per grid cell and per species
nPerSppPerGrid.2007.30 <- surveysObs1 %>%
  group_by(common_name, idCells) %>%
  mutate(observation_count = as.numeric(as.character(observation_count))) %>%
  summarise(nBirds = sum(observation_count), .groups = "drop") %>%
  spread(common_name, nBirds)
# 2,594 grid cells and 462 bird species

### Calculate the prevalence for each species. Here we are going to use only species present in the grid cells we will ultimately use.
nPerSppPerGrid.2007.30[is.na(nPerSppPerGrid.2007.30)] <- 0
nPerSppPerGrid.2007.30.col2toEnd <- nPerSppPerGrid.2007.30[ ,c(2:(dim(nPerSppPerGrid.2007.30)[2]))]
nPerSppPerGrid.2007.30.prev <- round(colSums(nPerSppPerGrid.2007.30.col2toEnd > 0) / nrow(nPerSppPerGrid.2007.30.col2toEnd), 4) * 100
species.2007.30 <- names(nPerSppPerGrid.2007.30.col2toEnd)
prev.2007.30 <- as.data.frame(cbind(species.2007.30, prev = nPerSppPerGrid.2007.30.prev))
prev.2007.30$prev <- as.numeric(as.character(prev.2007.30$prev))

### Export prevalence per species
write.csv(prev.2007.30, here("Data", "BioIndicator", "birdSpp_prevalences_30beeGrids_2007to2021_20231017.csv"), row.names = FALSE)

### Import file with percentage of our study area covered by the breeding range of each species
range.pct <- read.csv(here("Data", "BioIndicator", "pctOfEastHalfUSA_coveredByBirdRanges_20230511.csv"))

### Combine locations and study area prevalences for each range of years.
allPrevs.2007.30 <- merge(prev.2007.30, range.pct, by.x = "species.2007.30", by.y = "PRIMARY_COM_NAME")

write.csv(allPrevs.2007.30, here("Data", "BioIndicator", "prevalencesBirds_byLocations_byStudyArea_30beeGrids_2007to2021_20231017.csv"), row.names = FALSE)

remove(range.pct, nPerSppPerGrid.2007.30, nPerSppPerGrid.2007.30.col2toEnd, nPerSppPerGrid.2007.30.prev, allPrevs.2007.30)

```
&nbsp;     
 
#### Create a copy that has the zero filled data, using only species with at least 20% prevalence
```{r}

### Recreate two datasets: observations and checklists from merge dataset
ebd_surv <- surveysObs1 %>%
  select("latitude", "longitude", "observation_date", "time_observations_started", "observer_id",
                           "sampling_event_identifier", "protocol_code", "duration_minutes", "effort_distance_km",
                           "group_identifier", "state_code", "locality_id", "idCells") %>%
  distinct(sampling_event_identifier, .keep_all = TRUE)
# 377,830 checklists

surveysObs1 <- surveysObs1[, c("global_unique_identifier", "common_name", "scientific_name", "observation_count", "sampling_event_identifier")]
# 6,451,901 observations

### Save files, just in case!
saveRDS(surveysObs1, here("/Volumes/BirdsBees/Data/BioIndicator/eBirdObs_allBirds_EastUSA_2007to2021_20231017.rds"))
saveRDS(ebd_surv, here("/Volumes/BirdsBees/Data/BioIndicator/eBirdSamples_allBirds_EastUSA_2007to2021_20231017.rds"))

### Import list of species with at least 10% prevalence by locations of surveys and 40% prevalence by study area, if needed
prevalences.30 <- read.csv(here("Data", "BioIndicator", "prevalencesBirds_byLocations_byStudyArea_30beeGrids_2007to2021_20231017.csv"))
names(prevalences.30) <- c("CommonNames", "prev", "species", "pct.area")

### Check if some grassland species have prevalence just below 20%, for which their breeding distribution still covers 40% of study area
# test.30 <- prevalences.30[which(prevalences.30$pct.area >= 40),]

### Dickcissel, Grasshopper Sparrow, and Bobolink are grassland species (of interest)
spp.2007.30.prev <- prevalences.30$CommonNames[which(prevalences.30$prev >= 20 & prevalences.30$pct.area >= 40 | prevalences.30$CommonNames %in% c("Dickcissel", "Grasshopper Sparrow"))] # 88 species

### Remove birds of prey
flyovers <- c("American Kestrel", "Bald Eagle", "Broad-winged Hawk", "Chimney Swift", "Common Nighthawk", 
              "Cooper's Hawk", "Red-shouldered Hawk", "Red-tailed Hawk", "Turkey Vulture")
spp.2007.30.prev <- spp.2007.30.prev[spp.2007.30.prev %notin% flyovers] # 79 species

### Zero-fill the species and export file
ebd_zf <- surveysObs1 %>%
  group_by(common_name, sampling_event_identifier) %>%
  count() %>%
  ungroup() %>%
  complete(common_name, sampling_event_identifier, fill = list(n = 0)) %>%
  filter(common_name %in% spp.2007.30.prev) %>%  # I need to keep the checklists where these species are not detected.
  left_join(surveysObs1, by = c("common_name", "sampling_event_identifier")) %>%
  mutate(observation_count = ifelse(is.na(observation_count), 0, observation_count)) %>%
  select(sampling_event_identifier, common_name, observation_count) %>%
  left_join(ebd_surv, by = "sampling_event_identifier") %>%
  select(sampling_event_identifier, common_name, observation_count, latitude, longitude, observation_date, 
         observer_id, protocol_code, duration_minutes, effort_distance_km, time_observations_started, idCells) %>%
  group_by(common_name) %>%
  group_walk(~write.csv(.x, paste0("/Volumes/BirdsBees/Data/BioIndicator/eBirdObsSampl_2007to2021_min30beesCells/eBirdObsSampl_10prev_zf_", .y$common_name, "_atGridWith30Bees2Surv_EastUSA_2007to2021_20231017.csv"), row.names = FALSE))

```


